Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalnew\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-22 ms.tex
tdm edits

This enables a set of observed properties ($\left\{ x_i, \sigma_i \right\}$),
either spectroscopic, photometric,
or both, to define a likelihood function that may be sampled in
an MCMC chain:
\begin{equation}
\label{eq:ischochronelhood}
\ln \mathcal L(\boldsymbol{\theta}) \propto -\frac{1}{2} \displaystyle \sum_i \frac{\left(x_i -
  I_i\left(\boldsymbol{\theta} \right)\right)^2}{\sigma_i^2},
\end{equation}
where $I_i(\boldsymbol{\theta})$ is the isochrone model prediction of property
$i$ at the given parameters $\boldsymbol{\theta}$.
If the observed properties include any apparent magnitudes, then
$\boldsymbol{\theta}$ includes distance and extinction in addition
to mass, age, and \feh.

@@

\change{During the sampling process, we fit for galactic
extinction as one of our physical parameters.
For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
along that line of sight from the NASA/IPAC Extragalactic Database (NED), which reports the
\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
COBE/DIRBE and IRAS/ISSA.
The NED database returns the extinction in all relevant bandpasses except those used by
WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
We include the WISE bandpasses by applying the relative extinction values between
SDSS, 2MASS, and WISE calculated by \citet{Davenport14}.
In each step of our fitting process, we draw a value for $A_V$, calculate the expected extinction
in all bandpasses $A_X$, and then measure the likelihood of our model stellar fit to the
observed apparent magnitudes.
We apply a uniform prior ranging from zero to the obtained maximum extinction value and
marginalize over extinction in our final determination of stellar parameters. }

>>>>

This enables a set of observed properties ($\left\{ x_i, \sigma_i \right\}$),
either spectroscopic, photometric,
or both, to define a likelihood function to be sampled:
\begin{equation}
\label{eq:ischochronelhood}
\ln \mathcal L(\boldsymbol{\theta}) \propto -\frac{1}{2} \displaystyle \sum_i \frac{\left(x_i -
  I_i\left(\boldsymbol{\theta} \right)\right)^2}{\sigma_i^2},
\end{equation}
where $I_i(\boldsymbol{\theta})$ is the isochrone model prediction of property
$i$ at the given parameters $\boldsymbol{\theta}$.
If the observed properties include any apparent magnitudes, then
$\boldsymbol{\theta}$ includes distance and extinction in addition
to mass, age, and \feh.

@@

\change{During the sampling process, we fit for galactic
extinction as one of our physical parameters.
%For each star's position on the sky, we retrieve the calculated extinction at an infinite distance
%along that line of sight from the NASA/IPAC Extragalactic Database (NED), which reports the
%\citet{Schlafly11} recalibration of the \citet{Schlegel98} extinction map as measured by
%COBE/DIRBE and IRAS/ISSA.
%The NED database returns the extinction in all relevant bandpasses except those used by
%WISE, assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}.
We include the WISE bandpasses by applying the relative extinction values between
SDSS, 2MASS, and WISE calculated by \citet{Davenport14}.
In each step of our fitting process, we draw a value for $A_V$, calculate the expected extinction
in all bandpasses $A_X$ assuming the $R_V = 3.1$ reddening law of \citep{Fitzpatrick99}, 
and then measure the likelihood of our model stellar fit to the observed apparent magnitudes.
We apply a uniform prior ranging from zero to a maximum extinction value of 0.2 
(a conservative upper limit for a field at such high Galactic latitude), and
marginalize over extinction in our final determination of stellar parameters.}
